### 2017-01-29 experiments.tex
spelling

In one sense, the discovery curve improvements here are practically very useful, but not exremely large in a relative sense.  The SpiderMonkey curve has an APFD only slightly more than 2\% better than the best result from previous FPF efforts.  For GCC, APFD improves by 6.4\%.  However, the comparison is with the very \emph{best} curve chosen after running more than 16 different metrics.  In practice, users do not know ground truth to rank curves, thus Chen et al. \cite{PLDI13} do not really give a practical approach to distance metric selection in their PLDI work.  The best methods for different subjects varied widely, even in such difficult-to-understand ways as less-fine-grained coverage providing better results in some cases, but worse in other cases.   In practice, their work established that FPF could produce good curves, but gave very little useful guidance for choosing a metric for actual use of the technique.  It also included methods such as comparing output signatures that are inapplicable to differential testing in most cases, the most critical compiler application.  This paper presents a single curve using a universal metric, and achieves a 2-6\% percentage point improvement over the best of more than 16 different metrics studied in the previous work.  Moreover, the improvement is, for our subject programs, reliable:  choosing random subsets of the full data set, the difference in mean APFD is around 3\%, and statistically significant.

@@

Mutation cost reduction techniques are also applicable.  E.g., trivial compiler equivalence (TCE) \cite{TCE} can reject equivalent and redundant mutants, removing almost 30\% of mutants for benchmark subjects. Other techniques, such as using mutant schemas to avoid having to compile and store each mutant, are also applicable --- almost all of the techniques characterized by Offutt and Untch \cite{offutt2001mutation} as \emph{do faster} approaches apply.   Whether sampling mutants \cite{RahulISSRE} is applicable is less clear.  Even if the FPF curve remains the same, a critical mutant for localization might be omitted.  We performed some limited experiments, and found that for a few sample sizes ranging from 13\% of mutants to 50\% of mutants or using only some mutation operators (with the exception of operator-replacement-only), APFD was always better than PLDI 13 best.   However, the improvement in some cases was \emph{much} smaller than for the full set, and varied considerably (in some cases it was up to 2\% better than our full results).  Fault localization results were considerably worse, however (with relative rankings preserved) for both our techniques and MUSE/MUSEUM.  Finally, we have preliminary results indicating that a guided-sampling approach may provide good fuzzer taming (if not fault localizaton):  compute vectors over a small constant-sized \cite{RahulISSRE} sample of mutants, then report highly distinct failing tests.  Other metrics, such as coverage-based comparisons, could provide hints as to likely distinct tests (and thus mutants covered by them) to focus on first.  These are likely to be different faults.  After repairing some of these, choose mutants to evaluate that are covered by multiple tests with few or no repairing mutants (since such tests are the ones most likely to be distinct but not yet identified).  Such an approach could be quite cost-effective, requiring only a relatively small number of mutant evaluations before providing useful results.

>>>>

In one sense, the discovery curve improvements here are practically very useful, but not extremely large in a relative sense.  The SpiderMonkey curve has an APFD only slightly more than 2\% better than the best result from previous FPF efforts.  For GCC, APFD improves by 6.4\%.  However, the comparison is with the very \emph{best} curve chosen after running more than 16 different metrics.  In practice, users do not know ground truth to rank curves, thus Chen et al. \cite{PLDI13} do not really give a practical approach to distance metric selection in their PLDI work.  The best methods for different subjects varied widely, even in such difficult-to-understand ways as less-fine-grained coverage providing better results in some cases, but worse in other cases.   In practice, their work established that FPF could produce good curves, but gave very little useful guidance for choosing a metric for actual use of the technique.  It also included methods such as comparing output signatures that are inapplicable to differential testing in most cases, the most critical compiler application.  This paper presents a single curve using a universal metric, and achieves a 2-6\% percentage point improvement over the best of more than 16 different metrics studied in the previous work.  Moreover, the improvement is, for our subject programs, reliable:  choosing random subsets of the full data set, the difference in mean APFD is around 3\%, and statistically significant.

@@

Mutation cost reduction techniques are also applicable.  E.g., trivial compiler equivalence (TCE) \cite{TCE} can reject equivalent and redundant mutants, removing almost 30\% of mutants for benchmark subjects. Other techniques, such as using mutant schemas to avoid having to compile and store each mutant, are also applicable --- almost all of the techniques characterized by Offutt and Untch \cite{offutt2001mutation} as \emph{do faster} approaches apply.   Whether sampling mutants \cite{RahulISSRE} is applicable is less clear.  Even if the FPF curve remains the same, a critical mutant for localization might be omitted.  We performed some limited experiments, and found that for a few sample sizes ranging from 13\% of mutants to 50\% of mutants or using only some mutation operators (with the exception of operator-replacement-only), APFD was always better than PLDI 13 best.   However, the improvement in some cases was \emph{much} smaller than for the full set, and varied considerably (in some cases it was up to 2\% better than our full results).  Fault localization results were considerably worse, however (with relative rankings preserved) for both our techniques and MUSE/MUSEUM.  Finally, we have preliminary results indicating that a guided-sampling approach may provide good fuzzer taming (if not fault localization):  compute vectors over a small constant-sized \cite{RahulISSRE} sample of mutants, then report highly distinct failing tests.  Other metrics, such as coverage-based comparisons, could provide hints as to likely distinct tests (and thus mutants covered by them) to focus on first.  These are likely to be different faults.  After repairing some of these, choose mutants to evaluate that are covered by multiple tests with few or no repairing mutants (since such tests are the ones most likely to be distinct but not yet identified).  Such an approach could be quite cost-effective, requiring only a relatively small number of mutant evaluations before providing useful results.

### 2017-01-29 localizations.tex
spelling

This ranks a mutant $m$ (and associated statement) by the inverse of the distance
from $f$ to the most distant failng test also repaired by $m$, adding 1
so that if $m$ only repairs failures at distance 0 $r$ is well defined
(and maximal).
If $m$ does not repair $f$, it is not ranked at all.  One advantage of
this approach over some statistical methods is that by
ranking \emph{mutants} the localization offers developers not simply a
ranked statement but a kind of ``explanation'' \cite{GroceError} of the fault:  if \emph{this
mutant} were applied, the fault would not exhibit.  As Kochhar et
al. show \cite{Kochhar}, a large majority (more than 85\%) of developers considered
the ability of a localization tool to provide a \emph{rationale} or
reason for a localization important.  A mutation plus the tests that
stop failing when it is applied is a practical, concrete explanation
of a fault localization.  Mutants that repair a failure provide insight 
into the nature of the fault, and, we hypothesize, more information the 
closer they are to the center of the onion-ring.

>>>>

This ranks a mutant $m$ (and associated statement) by the inverse of the distance
from $f$ to the most distant failing test also repaired by $m$, adding 1
so that if $m$ only repairs failures at distance 0 $r$ is well defined
(and maximal).
If $m$ does not repair $f$, it is not ranked at all.  One advantage of
this approach over some statistical methods is that by
ranking \emph{mutants} the localization offers developers not simply a
ranked statement but a kind of ``explanation'' \cite{GroceError} of the fault:  if \emph{this
mutant} were applied, the fault would not exhibit.  As Kochhar et
al. show \cite{Kochhar}, a large majority (more than 85\%) of developers considered
the ability of a localization tool to provide a \emph{rationale} or
reason for a localization important.  A mutation plus the tests that
stop failing when it is applied is a practical, concrete explanation
of a fault localization.  Mutants that repair a failure provide insight 
into the nature of the fault, and, we hypothesize, more information the 
closer they are to the center of the onion-ring.
